19Q1

### 2019-03-15 19Q1.Rmd

19Q1 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
```{r}
ccl_info <- read.delim("./data_munging/19Q1/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
ccl_info$source <- "CCLE"
ccl_info$source_ccl_name <- strsplit(as.character(ccl_info$CCLE_Name), split = "_")
ccl_info$source_ccl_name <- as.character(lapply(ccl_info$source_ccl_name, function(x) ifelse("[MERGED" %in% x || "NORMAL" %in% x, NA, x[1])))
ccl_info$source_ccl_name[ccl_info$source_ccl_name == "NA"] <- NA
ccl_info$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccl_info$CCLE_Name, ignore.case = TRUE))
ccl_info$source_histology <- ifelse(ccl_info$CCLE_Name == ccl_info$source_ccl_name, NA, ccl_info$source_histology)
ccl_info$sample_id <- with(ccl_info, paste(source, source_ccl_name, source_histology, sep = "_"))
# This CCL had a histology of "primary": Looking at the DepMap reference, this is an immortalize epithelial line from the CNS (https://depmap.org/portal/cell_line/NHAHTDD_PRIMARY), so I chanegd the histology accordingly
ccl_info$source_histology[ccl_info$source_ccl_name == "NHAHTDD"] <- "central_nervous_system"
# Convert Primary.Disease entries to all lower case to fix factorization issue
ccl_info$Primary.Disease <- as.factor(tolower(ccl_info$Primary.Disease))
# Harmonize ID column name
colnames(ccl_info)[colnames(ccl_info) == "DepMap_ID"] <- "Broad_ID"

@@

pgx_ccle_ge <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_id, Broad_ID), ge_19Q1, by = "Broad_ID", all = TRUE)

# Melt
ge_melt_19Q1 <- melt(ge_19Q1, id.vars = "Broad_ID", measure.vars = colnames(ge_19Q1)[2:ncol(ge_19Q1)], variable.name = "Hugo_Symbol", value.name = "TPM")
# ge_melt_19Q1 <- unique(ge_melt_19Q1_all)

saveRDS(pgx_ccle_ge, "./data_munging/19Q1/pgx_ccle_ge.rds", compress = "xz")
saveRDS(ge_melt_19Q1, "./data_munging/19Q1/ge_melt_19Q1.rds", compress = "xz")
```

@@

Code for Denise's graph convolutional networks analyses (see meeting notes from 6 March 2019).
- Convert drug/compound names to all capitalized for harmonization.
- Convert all cell line histologies to lower case with words separated by an underscore
- Maintain same rows across all four data frames, filling with NAs as necessary
- For each dataframe, maintain same columns for all three source datasets
- Columns in final dataframes: `source`, `source_ccl_name`, `source_histology`, `sample_id`, and `genes/compounds/mutations[p]`

@@

- `source`: the dataset from which the data comes from (either CCLE, CTRP, or GDSC)
- `source_ccl_name`: the name of the cancer cell line (CCL) included in the source dataset
    - Note that all CCLs (excluding matched normal tissues and "merged" CCLs) from the CCLE dataset (N = 1,645) were included in `pgx_all_auc` for imputation
- `source_histology`: the general histology/tissue type of the CCL
- `sample_id`: custom identifiers for our datasets that are concatenations of the `source`, `source_ccl_name`, and `source_histology`
- All other columns: compound and drug names that were screened in at least one CCL in at least one source dataset
    - NA values indictate that compound wasn't screened in the respective CCL in the respective source dataset

@@

# CCLE
## Note that ActArea is NOT an AUC value
ccle_filt <- ccle[, c("CCLE Cell Line Name", "ActArea", "Compound")]
ccle_filt$source_ccl_name <- sapply(strsplit(as.character(ccle_filt$`CCLE Cell Line Name`), split = "_"), function(x) x[1])
ccle_filt$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccle_filt$`CCLE Cell Line Name`, ignore.case = TRUE))
ccle_filt$source_histology <- ifelse(ccle_filt$`CCLE Cell Line Name` == ccle_filt$source_ccl_name, NA, ccle_filt$source_histology)
ccle_filt <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_id), ccle_filt, by = c("source_ccl_name", "source_histology"), all = TRUE)
ccle_filt$compound_name <- toupper(ccle_filt$Compound)
colnames(ccle_filt)[colnames(ccle_filt) == "ActArea"] <- "AUC"
ccle_auc_long <- select(ccle_filt, source, source_ccl_name, source_histology, sample_id, compound_name, AUC)
# ccle_auc_long$source <- "CCLE"
# ccle_auc_long$sample_id <- with(ccle_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
ccle_auc <- dcast(ccle_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
ccle_auc[, 5:ncol(ccle_auc)] <- ccle_auc[, 5:ncol(ccle_auc)] %>% replace_with_na_all(condition = ~.x == 10000)

# CTRP
## area_under_curve: integrated area under the sigmoid-fit concentration-response curve
ctrp_filt <- ctrp[, c("experiment_id", "area_under_curve", "master_cpd_id")]
ctrp_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_cell_line_20190306.txt"), master_ccl_id, ccl_name, ccle_primary_site)
ctrp_meta_exp <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_experiment_20190306.txt"), experiment_id, master_ccl_id)
ctrp_meta_cpd <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_compound_20190306.txt"), master_cpd_id, cpd_name)
ctrp_keep <- merge(merge(ctrp_meta_ccl, ctrp_meta_exp, by = "master_ccl_id", all = TRUE), merge(ctrp_meta_cpd, ctrp_filt, by = "master_cpd_id", all = TRUE), by = "experiment_id", all = TRUE)
ctrp_keep$ccl_name <- gsub("-", "", ctrp_keep$ccl_name, ignore.case = TRUE)
ctrp_keep$cpd_name <- toupper(ctrp_keep$cpd_name)
ctrp_keep$ccle_primary_site <- ifelse(as.character(ctrp_keep$ccle_primary_site) == "", NA, as.character(ctrp_keep$ccle_primary_site))
ctrp_auc_long <- select(ctrp_keep, ccl_name, ccle_primary_site, cpd_name, area_under_curve)
colnames(ctrp_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
ctrp_auc_long$source <- "CTRP"
ctrp_auc_long$sample_id <- with(ctrp_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
ctrp_auc_long_div <- ctrp_auc_long
ctrp_auc_long_div$AUC <- ctrp_auc_long_div$AUC / 100
ctrp_auc <- dcast(ctrp_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
ctrp_auc[, 5:ncol(ctrp_auc)] <- ctrp_auc[, 5:ncol(ctrp_auc)] %>% replace_with_na_all(condition = ~.x == 10000)

# GDSC
gdsc_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_Cell_Lines_Details.csv", sep = ","), Line, Site)
## For following 4 Lines, Site == "NS"
## Assigned new Sites by looking up cell lines in GDSC cell line portal (https://www.cancerrxgene.org/translation/CellLine#t-all)
gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "COR-L321"] <- "lung"
gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "SU-DHL-8"] <- "haematopoietic_and_lymphoid_tissue"
gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "CRO-AP3"] <- "haematopoietic_and_lymphoid_tissue"
gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "Hep_3B2_1-7"] <- "liver"
## For tollowing line, Site did not match CCLE notation, so I changed it to CCLE notation
gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "SW13"] <- "adrenal_cortex"
gdsc_filt <- gdsc[, c("CELL_LINE_NAME", "DRUG_NAME", "AUC")]
gdsc_filt$DRUG_NAME <- toupper(gdsc_filt$DRUG_NAME)
colnames(gdsc_filt)[colnames(gdsc_filt) ==  "CELL_LINE_NAME"] <- "Line"
gdsc_filt <- merge(gdsc_filt, gdsc_meta_ccl, by = "Line", all = TRUE)
gdsc_filt$Line <- gsub("-", "", gdsc_filt$Line, ignore.case = TRUE)
gdsc_auc_long <- select(gdsc_filt, Line, Site, DRUG_NAME, AUC)
colnames(gdsc_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
gdsc_auc_long$source <- "GDSC"
gdsc_auc_long$sample_id <- with(gdsc_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
gdsc_auc_long$source_histology <- as.character(gdsc_auc_long$source_histology)
gdsc_auc <- dcast(gdsc_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
gdsc_auc[, 5:ncol(gdsc_auc)] <- gdsc_auc[, 5:ncol(gdsc_auc)] %>% replace_with_na_all(condition = ~.x == 10000)

@@

### GE

```{r, eval=FALSE}
ge_melt <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")
ge_merged <- merge(select(ccl_info, Broad_ID, source_histology, source_ccl_name), ge_melt, by = "Broad_ID", all = TRUE)
```

### CN

```{r, eval=FALSE}
cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
```

### Mut

```{r, eval=FALSE}
maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
```

@@

>>>>

19Q1 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
```{r}
ccl_info <- read.delim("./data_munging/19Q1/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
ccl_info$source <- "CCLE"
ccl_info$source_ccl_name <- strsplit(as.character(ccl_info$CCLE_Name), split = "_")
ccl_info$source_ccl_name <- as.character(lapply(ccl_info$source_ccl_name, function(x) ifelse("[MERGED" %in% x || "NORMAL" %in% x, NA, x[1])))
ccl_info$source_ccl_name[ccl_info$source_ccl_name == "NA"] <- NA
ccl_info$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccl_info$CCLE_Name, ignore.case = TRUE))
ccl_info$source_histology <- ifelse(ccl_info$CCLE_Name == ccl_info$source_ccl_name, NA, ccl_info$source_histology)
ccl_info$sample_ID <- with(ccl_info, paste(source, source_ccl_name, source_histology, sep = "_"))
# This CCL had a histology of "primary": Looking at the DepMap reference, this is an immortalize epithelial line from the CNS (https://depmap.org/portal/cell_line/NHAHTDD_PRIMARY), so I chanegd the histology accordingly
ccl_info$source_histology[ccl_info$source_ccl_name == "NHAHTDD"] <- "central_nervous_system"
# Convert Primary.Disease entries to all lower case to fix factorization issue
ccl_info$Primary.Disease <- as.factor(tolower(ccl_info$Primary.Disease))
# Harmonize ID column name and rename CCLE_Name column to fit with dataframe style
colnames(ccl_info)[colnames(ccl_info) == "CCLE_Name"] <- "CCLE_ccl_name"
colnames(ccl_info)[colnames(ccl_info) == "DepMap_ID"] <- "Broad_ID"

@@

# For Denise's GCN
pgx_ccle_ge <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_ID, CCLE_ccl_name, Broad_ID), ge_19Q1, by = "Broad_ID", all = TRUE)
saveRDS(pgx_ccle_ge, "./data_munging/19Q1/pgx_ccle_ge.rds", compress = "xz")

# Melt
ge_melt_19Q1 <- melt(ge_19Q1, id.vars = "Broad_ID", measure.vars = colnames(ge_19Q1)[2:ncol(ge_19Q1)], variable.name = "Hugo_Symbol", value.name = "TPM")
# ge_melt_19Q1 <- unique(ge_melt_19Q1_all)
saveRDS(ge_melt_19Q1, "./data_munging/19Q1/ge_melt_19Q1.rds", compress = "xz")
```

@@

Code for Denise's graph convolutional networks analyses (see meeting notes from 6 March 2019).
- Convert drug/compound names to all capitalized for harmonization.
- Convert all cell line histologies to lower case with words separated by an underscore
- Maintain same rows across all four data frames, filling with NAs as necessary
- For each dataframe, maintain same columns for all three source datasets
- Columns in final dataframes: `source`, `source_ccl_name`, `source_histology`, `sample_ID`, and `genes/compounds/mutations[p]`

@@

- `source`: the dataset from which the data comes from (either CCLE, CTRP, or GDSC)
- `source_ccl_name`: the name of the cancer cell line (CCL) included in the source dataset
    - Note that all CCLs (excluding matched normal tissues and "merged" CCLs) from the CCLE dataset (N = 1,645) were included in `pgx_all_auc` for imputation
- `source_histology`: the general histology/tissue type of the CCL
- `sample_ID`: custom identifiers for our datasets that are concatenations of the `source`, `source_ccl_name`, and `source_histology`
- `CCLE_ccl_name`: the cell line name using CCLE nomenclature, which is a concatenation of the cell line name with the CCLE-annotated histology in all caps, separated by underscores
- `Broad_ID`: the custom identifiers (formatted as ACH-######) used by the Broad's Cancer Dependency Map project to ease cell line name harmonization efforts 
- All other columns: compound and drug names that were screened in at least one CCL in at least one source dataset
    - NA values indictate that compound wasn't screened in the respective CCL in the respective source dataset

@@

# CCLE
## Note that ActArea is NOT an AUC value
ccle_filt <- ccle[, c("CCLE Cell Line Name", "ActArea", "Compound")]
ccle_filt$source_ccl_name <- sapply(strsplit(as.character(ccle_filt$`CCLE Cell Line Name`), split = "_"), function(x) x[1])
ccle_filt$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccle_filt$`CCLE Cell Line Name`, ignore.case = TRUE))
ccle_filt$source_histology <- ifelse(ccle_filt$`CCLE Cell Line Name` == ccle_filt$source_ccl_name, NA, ccle_filt$source_histology)
colnames(ccle_filt)[colnames(ccle_filt) == "CCLE Cell Line Name"] <- "CCLE_ccl_name"
ccle_filt <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_ID, CCLE_ccl_name, Broad_ID), ccle_filt, by = c("source_ccl_name", "source_histology", "CCLE_ccl_name"), all = TRUE)
ccle_filt$compound_name <- toupper(ccle_filt$Compound)
colnames(ccle_filt)[colnames(ccle_filt) == "ActArea"] <- "AUC"
ccle_auc_long <- select(ccle_filt, source, source_ccl_name, source_histology, sample_ID, CCLE_ccl_name, Broad_ID, compound_name, AUC)
ccle_auc <- dcast(ccle_auc_long, source + source_ccl_name + source_histology + sample_ID + CCLE_ccl_name + Broad_ID ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
ccle_auc[, 7:ncol(ccle_auc)] <- ccle_auc[, 7:ncol(ccle_auc)] %>% replace_with_na_all(condition = ~.x == 10000)

# CTRP
## area_under_curve: integrated area under the sigmoid-fit concentration-response curve
ctrp_filt <- ctrp[, c("experiment_id", "area_under_curve", "master_cpd_id")]
ctrp_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_cell_line_20190306.txt"), master_ccl_id, ccl_name, ccle_primary_site)
ctrp_meta_exp <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_experiment_20190306.txt"), experiment_id, master_ccl_id)
ctrp_meta_cpd <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_compound_20190306.txt"), master_cpd_id, cpd_name)
ctrp_keep <- merge(merge(ctrp_meta_ccl, ctrp_meta_exp, by = "master_ccl_id", all = TRUE), merge(ctrp_meta_cpd, ctrp_filt, by = "master_cpd_id", all = TRUE), by = "experiment_id", all = TRUE)
ctrp_keep$ccl_name <- gsub("-", "", ctrp_keep$ccl_name, ignore.case = TRUE)
ctrp_keep$cpd_name <- toupper(ctrp_keep$cpd_name)
ctrp_keep$ccle_primary_site <- ifelse(as.character(ctrp_keep$ccle_primary_site) == "", NA, as.character(ctrp_keep$ccle_primary_site))
ctrp_auc_long <- select(ctrp_keep, ccl_name, ccle_primary_site, cpd_name, area_under_curve)
colnames(ctrp_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
ctrp_auc_long$source <- "CTRP"
ctrp_auc_long$sample_ID <- with(ctrp_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
ctrp_auc_long <- merge(ctrp_auc_long, select(ccl_info, source_ccl_name, source_histology, CCLE_ccl_name, Broad_ID), by = c("source_ccl_name", "source_histology"), all.x = TRUE)
ctrp_auc_long_div <- ctrp_auc_long
ctrp_auc_long_div$AUC <- ctrp_auc_long_div$AUC / 100
ctrp_auc <- dcast(ctrp_auc_long, source + source_ccl_name + source_histology + sample_ID + CCLE_ccl_name + Broad_ID ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
ctrp_auc[, 7:ncol(ctrp_auc)] <- ctrp_auc[, 7:ncol(ctrp_auc)] %>% replace_with_na_all(condition = ~.x == 10000)

# GDSC
gdsc_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_Cell_Lines_Details.csv", sep = ","), Line, Site)
## For following 4 Lines, Site == "NS"
## Assigned new Sites by looking up cell lines in GDSC cell line portal (https://www.cancerrxgene.org/translation/CellLine#t-all)
gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "COR-L321"] <- "lung"
gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "SU-DHL-8"] <- "haematopoietic_and_lymphoid_tissue"
gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "CRO-AP3"] <- "haematopoietic_and_lymphoid_tissue"
gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "Hep_3B2_1-7"] <- "liver"
## For tollowing line, Site did not match CCLE notation, so I changed it to CCLE notation
gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "SW13"] <- "adrenal_cortex"
gdsc_filt <- gdsc[, c("CELL_LINE_NAME", "DRUG_NAME", "AUC")]
gdsc_filt$DRUG_NAME <- toupper(gdsc_filt$DRUG_NAME)
colnames(gdsc_filt)[colnames(gdsc_filt) ==  "CELL_LINE_NAME"] <- "Line"
gdsc_filt <- merge(gdsc_filt, gdsc_meta_ccl, by = "Line", all = TRUE)
gdsc_filt$Line <- gsub("-", "", gdsc_filt$Line, ignore.case = TRUE)
gdsc_auc_long <- select(gdsc_filt, Line, Site, DRUG_NAME, AUC)
colnames(gdsc_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
gdsc_auc_long$source <- "GDSC"
gdsc_auc_long$sample_ID <- with(gdsc_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
gdsc_auc_long$source_histology <- as.character(gdsc_auc_long$source_histology)
gdsc_auc_long <- merge(gdsc_auc_long, select(ccl_info, source_ccl_name, source_histology, CCLE_ccl_name, Broad_ID), by = c("source_ccl_name", "source_histology"), all.x = TRUE)
gdsc_auc <- dcast(gdsc_auc_long, source + source_ccl_name + source_histology + sample_ID + CCLE_ccl_name + Broad_ID ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
gdsc_auc[, 7:ncol(gdsc_auc)] <- gdsc_auc[, 7:ncol(gdsc_auc)] %>% replace_with_na_all(condition = ~.x == 10000)

@@

@@

### Pozdeyev et al. (2016)

```{r}
ccl_histologies <- select(ccl_info, source_ccl_name, source_histology) %>% drop_na(source_ccl_name)
colnames(ccl_histologies)[colnames(ccl_histologies) == "source_ccl_name"] <- "Cell_line" 
auc <- read.delim("./data_munging/pharmacogenomics_raw_files/celline_stack.csv.gz", sep = ",")
auc <- merge(ccl_histologies, auc, by = "Cell_line", all.y = TRUE)
num_auc_per_db <- auc %>% count(Database)
num_ccl_per_db <- unique(select(auc, Database, Cell_line)) %>% count(Database)
# only CCLs represetented in 2 or 3 databases were included
num_db_per_ccl <- unique(select(auc, Database, Cell_line)) %>% count(Cell_line)
```

There were `r length(setdiff(unique(ccl_histologies$Cell_line), unique(auc$Cell_line)))` cell lines not represented in the Pozdeyev et al. harmonized dataset.

Plots:
```{r}
futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
venn_ccl_pozdeyev <- venn.diagram(list("CCLE" = unique(filter(ccl_per_db, Database == "CCLE"))$Cell_line, "CTRP" = unique(filter(ccl_per_db, Database == "CTRP"))$Cell_line, "GDSC" = unique(filter(ccl_per_db, Database == "GDSC"))$Cell_line), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
png("./gcn_denise/pozdeyev_venn_ccl.png")
grid.newpage()
grid.draw(venn_ccl_pozdeyev)
dev.off()

num_ccl_per_db_bar <- ggplot(data = unique(select(auc, Database, Cell_line))) +
  geom_bar(aes(x = Database, fill = Database), alpha = 0.7) +
  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) + 
  guides(fill = "none") +
  scale_y_continuous(breaks = seq(0, 700, by = 50), labels = seq(0, 700, by = 50)) +
  geom_text(data = num_ccl_per_db, aes(x = Database, y = n + 20, label = n)) +
  labs(y = "Number of cell lines", title = "Number of unique cell lines per dataset")
ggsave("./gcn_denise/pozdeyev_ccl_per_db.png", num_ccl_per_db_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")

num_ccl_per_hist_bar <- ggplot(data = unique(select(auc, Database, Cell_line, source_histology))) +
  facet_wrap(~ Database, scales = "free_y") +
  geom_bar(aes(x = source_histology, fill = source_histology), alpha = 0.7) +
  guides(fill = "none") +
  coord_cartesian(ylim = c(0, 130)) +
  scale_y_continuous(breaks = seq(0, 130, by = 10), labels = seq(0, 130, by = 10)) +
  labs(x = "Histology", y = "Number of cell lines", title = "Number of unique cell lines per histology") +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
ggsave("./gcn_denise/pozdeyev_ccl_per_histology.png", num_ccl_per_hist_bar, device = "png", dpi = 450, width = 12, height = 6, units = "in")

auc_per_db_dist <- ggplot(data = auc) +
  facet_wrap(~ Database) +
  geom_histogram(aes(x = AUC_IC50, fill = Database), color = "black", alpha = 0.7, binwidth = 0.025, boundary = 0, closed = "left") +
  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
  guides(fill = "none") +
  geom_text(data = num_auc_per_db, aes(x = 0.5, y = 4750, label = paste0("n = ", formatC(n, format = "d", big.mark = ",")))) +
  scale_y_continuous(breaks = seq(0, 5000, by = 500), labels = seq(0, 5000, by = 500)) +
  labs(x = "AUC IC50", y = "Frequency", title = "Distributions of AUC IC50 values for all drugs in each dataset")
ggsave("./gcn_denise/pozdeyev_aucic50_per_db_dist.png", auc_per_db_dist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
```
